What We Eval in the Shadows

### 2021-08-06 paper/main.tex
Add alternative to \eval

\subsection{Alternatives to \eval}
Talk about lazyeval and tidyeval

@@

>>>>

@@

\subsection{Alternatives to \eval}

An alternative implementation of \eval, \c{eval\_tidy}, is provided by the
\c{rlang} package. This forms the base of the tidy evaluation framework used by
the libraries collectively referred to as the \c{tidyverse}~\cite{tidyverse}. It
differs from the \c{eval} function in two ways. First, it supports evaluation of
Quosures, which are also custom objects used by the \c{tidyverse} libraries for
metaprogramming. Quosures package expression with an evaluation environment. The
\c{tidy\_eval} function extracts this expression and evaluates it in that
environment, ignoring the environment passed to it explicitly as an argument.
Second, the \c{eval\_tidy} function also accepts a data mask argument.This is a
set of bindings supplied by the user as a data frame or a named vector or list.
The data mask environment take precedence over the environment passed for
evaluation. Since the expression is always evaluated in the data mask, it has
different semantics compared to \c{base::eval}. Effects such as assignment using
\c{<-} happen in the data mask environment. Expressions such as \c{return()} do
not work since the data mask environment does not correspond to a frame on the
call stack.
